%-------------------------
% Resume in Latex
% Author : Vaishanth
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}

\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}%\setmainfont{Times New Roman}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% \usepackage[T1]{fontenc}
% \usepackage[T1]{fontenc}
% \usepackage{cochineal}
% \usepackage{fourier}

% \usepackage{fontspec}
% \usepackage{polyglossia}
% \setmainlanguage{german}
% \setmainfont{Times New Roman}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}

\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSingleSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-5pt}\item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}\\ % Đã đổi \textbf thành \textit để giống Experience
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeHonorHeading}[2]{
    \vspace{-8pt}\item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeHonorListStart}{\begin{itemize}[leftmargin=0.0in, label={}, itemsep=-4pt, parsep=0pt]}
\newcommand{\resumeHonorListEnd}{\end{itemize}}
\newcommand{\resumeProjectListStart}{\begin{itemize}[leftmargin=0.0in, label={}, itemsep=-6pt, parsep=0pt]}
\newcommand{\resumeProjectListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.1in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------\usepackage{fontspec}
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING----------

\begin{center}
    {\huge \textbf{Minh (Drake) Pham}} \\ \vspace{5pt} 
    \small
    \href{tel:+84962763170}{(+84) 962763170} ~ \small{-}
    \href{mailto:hadtnt71@gmail.com}{hadtnt71@gmail.com} ~ \small{-}
    \href{https://www.linkedin.com/in/drakempham/}{linkedin.com/in/drakempham} \\ \vspace{2pt}
    \href{https://github.com/drakempham}{github.com/drakempham} ~ \small{-}
    \href{https://leetcode.com/u/drakempham/}{leetcode.com/u/drakempham}
    \vspace{-7pt}
\end{center}

%-----------SUMMARY-----------
\section{\color{airforceblue}SUMMARY}

\resumeSubHeadingListStart
    \item[] \small{ % Use \item[] to suppress bullet
        6+ years Experienced Engineer • VNU-HCMUS Computer Science Graduate. \\
        Delivering 10+ production projects across FinTech, banking, transportation, and charity sectors. \\
        Specialized in building scalable, high-performance applications with deep expertise in algorithms, data structures, and modern architectures. \\Versatile background as a Full-Stack, DevOps including research and B2B/B2C product delivery.\\
    }
\resumeSubHeadingListEnd

\vspace{-10pt} % Adjust if needed; smaller than -15pt to avoid over-pull

%-----------EDUCATION-----------
\section{\color{airforceblue}EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {VNUHCM - University of Science}{Ho Chi Minh City, Vietnam}
      {Bachelor of Computer Science}{Sep 2019 -- Sep 2023}
      \resumeItemListStart
        \item[] \small{GPA: 3.7/4.0}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{\color{airforceblue}TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{\normalsize{Programming Languages:}}{ \normalsize{Python, C++, Java (Spring Boot), Golang, Ruby, CUDA (Nvidia) }} \\
      \vspace{1.2pt}
      
     \textbf{\normalsize{Distributed Systems \& Middleware:}}{ \normalsize{Kafka, Redis, ActiveMQ, Microservices, Message Queues}} \\
      \vspace{1.2pt}
      
     \textbf{\normalsize{Databases \& Storage:}}{ \normalsize{MySQL, TiDB, PostgreSQL, MongoDB}} \\
      \vspace{1.2pt}
      
     \textbf{\normalsize{Cloud Platform\& Infrastructure:}}{ \normalsize{AWS Lambda, Google Cloud Functions, Azure Functions, Docker, Git, CI/CD Pipelines}}
    }}
 \end{itemize}
 \vspace{-16pt}
 
 
%-----------WORK EXPERIENCE-----------
\section{\color{airforceblue}WORK EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
  {Infrastructure Engineer -- Core Payment Engine}{Ho Chi Minh City, VN}
  {VNG Corporation (ZaloPay)\href{https://github.com/drakempham/Scale-30M-users-infra}{ - GitHub: Scale-30M-users-infra}}{06/2024 -- Present}
        \resumeItem{Engineered a distributed data pipeline using Apache Kafka and Spark to process 1TB+ of daily transaction logs; implemented multi-threaded prefetching and sharding, reducing GPU starvation by 20\% and accelerating model training cycles by 1.3x.}
        \resumeItem{Engineered high-throughput transaction infrastructure handling 1,000+ peak TPS with low-latency optimizations.}
        \resumeItem{Optimized MySQL and Kafka architectures to maintain highly reliable, distributed payment systems.}
        \resumeItem{\normalsize{Designed and implemented a Saga-based transaction engine using State Machines to ensure atomicity and recoverability; handled complex states (start, processing, waiting, recovery) to resolve failed-at-half transactions.}}
        \resumeItem{\normalsize{Developed idempotent payment order processing to prevent double-charging during network retries and timeouts, ensuring system correctness at 1,000+ peak TPS.}}
        \resumeItem{\normalsize{Implemented a Hook Handler system to decouple cross-cutting concerns like logging, auditing, and notifications from the core business flows.}}
        \resumeItem{\normalsize{Optimized distributed consistency and observability by using Sonyflake for collision-free, time-ordered unique ID generation with B3 Tracing for cross-service context propagation, ensuring 100\% request lineage across the payment lifecycle.}}
        \resumeItem{\normalsize{Centralized and optimized the ZAS database architecture by consolidating fragmented systems into a unified, high-performance data space.}}
        \resumeItem{\normalsize{Designed and deployed automated refund APIs to handle transaction failures or timeouts, ensuring financial consistency.}}
        \resumeItem{\normalsize{Mentored new fresher during onboarding, facilitating knowledge transfer, accelerating ramp-up, and ensuring smooth integration into the team.}}
        
      \resumeItemListEnd

    \resumeSubheading
      {Backend Engineer -- Booking and Payment Taxi System}{Ho Chi Minh City, Vietnam}
      {FPT Software}{10/2023 -- 06/2024}
      \resumeItemListStart
        \resumeItem{\normalsize{Developed server-side logic for high-performance microservices (Payment, OpenAPI, SMS, IVR), contributing to a 16\% increase in website traffic and conversion rates.}}
        \resumeItem{\normalsize{Optimized scalability by improving asynchronous processing with Kafka, Schema Registry, and RedisMQ; implemented advanced consumption strategies to handle blocking errors and ordering.}}
        \resumeItem{\normalsize{Deployed and monitored services across SIT, UAT, and Production environments using CloudWatch, CodePipeline, and Grafana.}}
        \resumeItem{\normalsize{Migrated approximately 1 million records between upstream and downstream databases using AWS Glue (ETL), Lambda, and S3 notifications.}}
      \resumeItemListEnd

    \resumeSubheading
      {Fullstack Engineer}{Ho Chi Minh City, Vietnam}
      {KMS Technology}{Sep 2022 -- Oct 2023}
      \resumeItemListStart
        \resumeItem{\normalsize{Demonstrated strong attention to detail in full-stack development, helping reduce system-side production errors by approximately 25\%.}}
      \resumeItemListEnd

    % \resumeSubheading
    %   {Teaching Assistant}{Ho Chi Minh City, Vietnam}
    %   {Kmin Academy}{Aug 2022 -- Aug 2025}
    %   \resumeItemListStart
    %     \resumeItem{\normalsize{Guided students in mastering Core CS concepts and Full-stack development, resulting in improved academic performance and project quality.}}
    %     \resumeItem{\normalsize{Collaborated with instructors to develop and refine technical course materials, assignments, and assessments for optimized learning.}}
    %     \resumeItem{\normalsize{Facilitated study sessions and provided detailed technical feedback on student projects to bridge the gap between theory and practice.}}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-12pt}


%-----------PROJECTS-----------
\section{\color{airforceblue}PROJECTS}
  \resumeProjectListStart

    % Project 1
    \resumeProjectHeading
    {\textbf{cuBLAS Worklog: Hardware-Aware GEMM Optimization} $|$ \emph{CUDA C++, PTX, Tesla T4 - Colab, Nsight Compute}} {2025}
   \resumeItemListStart
        \resumeItem{\normalsize{Medium paper: \href{https://medium.com/@minhdrake/cublas-worklog-hardware-aware-gemm-optimization-for-nvidia-tensor-cores-ddf2712a6a33}{CuBLAS Worklog Hardware-Aware GEMM Optimization for NVIDIA Tensor Core}}}
        \resumeItem{\normalsize{Engineered an 11-stage architectural optimization worklog, systematically transforming a memory-bound scalar baseline into high-performance pipelines yielding $\sim$4.0 TFLOP/s for FP32 (90\% of cuBLAS) and 17.06 TFLOP/s for mixed-precision (FP16/FP32) Tensor Cores.}}
        \resumeItem{\normalsize{Dismantled the HBM memory-wall and bypassed shared-memory scatter overhead by architecting 128$\times$128 hardware-aligned block tiles, 128-bit \texttt{int4} global memory vectorization, and PTX \texttt{ldmatrix} zero-overhead register staging.}}
        \resumeItem{\normalsize{Profiled microarchitectural constraints (warp stalls, instruction pressure) via Nsight Compute to double active warp rates to 49.4\% SM occupancy, delivering a massive 36$\times$ overall throughput speedup on an NVIDIA T4 GPU.}}
    \resumeItemListEnd
    % Project 2
    \resumeProjectHeading
    {\textbf{nanoGPT Token Predictor (v1)} $|$ \emph{Python, PyTorch, Transformer Architecture} $|$ \href{https://github.com/danepham2204/nanoGPT-Token-Prediction}{GitHub link}} {2025 - 2026}
    \resumeItemListStart
        \resumeItem{\normalsize{Engineered a character-level Generative Pre-trained Transformer (GPT) from scratch, evolving a naive Bigram baseline into a deep architecture powered by Multi-Head Self-Attention and Layer Normalization.}}
        \resumeItem{\normalsize{Architected the autoregressive generation pipeline utilizing scaled dot-product attention with causal triangular masking to prevent forward-looking data leakage during sequence modeling.}}
        \resumeItem{\normalsize{Trained a $\sim$0.21M parameter network on the Tiny Shakespeare dataset via AdamW optimization, driving cross-entropy loss down by 62\% (from 4.41 to 1.66) and successfully capturing character-level grammatical structures.}}
    \resumeItemListEnd

    % Project 1
    \resumeProjectHeading
    {\textbf{Fault-Tolerant Stream Processing with Exactly-Once Semantics} $|$ \emph{Kafka, Docker, Java}} {2025 - 2026}
    \resumeItemListStart
        \resumeItem{\normalsize{Engineered a fault-tolerant pipeline using Kafka Transactions (KIP-98) and atomic Consume-Transform-Produce pattern, solving the distributed "dual-write" problem without external state stores.}}
        \resumeItem{\normalsize{Deep-dived into Producer internals to implement Offset-Transaction Binding, ensuring the input offset commit and output message visibility occur atomically or not at all (Atomic Commit).}}
        \resumeItem{\normalsize{Validated system integrity via Chaos Engineering: injected random process crashes during active transactions, achieving 100\% data accuracy (Zero Duplicates/Loss) upon recovery.}}
    \resumeItemListEnd

    % Project 3
    \resumeProjectHeading
      {\textbf{Asset Exchange V2} $|$ \small{Java, Kafka, MySQL, Redis, gRPC/REST, Kubernetes, OpenSearch}}{2024 - 2026}
      \resumeItemListStart
        \resumeItem{\normalsize{Architected a high-throughput asset exchange engine based on saga context and state machine, ensuring strict atomicity for cross-channel fund movements using a Saga-based orchestration.}}
        \resumeItem{\normalsize{Strengthened system resilience by implementing a multi-tier retry strategy and Dead Letter Queues (DLQ) in Kafka, ensuring zero data loss and automated recovery during intermittent failures.}}
        \resumeItem{\normalsize{Ensured data consistency between MySQL and Kafka by adopting the Transactional Outbox pattern, guaranteeing that every financial state change is reliably published and processed.}}
        \resumeItem{\normalsize{Successfully mitigated Kafka consumer lag issues during high-traffic periods by scaling topic partitions and optimizing consumer-side processing logic, significantly improving message throughput.}}
      \resumeItemListEnd

    % % Project 3
    % \resumeProjectHeading
    %   {\textbf{Asset Exchange V2} $|$ \small{Java, Kafka, MySQL, Redis, gRPC/REST, Kubernetes, OpenSearch}}{2024 -- Present}
    %   \resumeItemListStart
    %     \resumeItem{\normalsize{Architected a high-throughput asset exchange engine based on saga context and state machine, ensuring strict atomicity for cross-channel fund movements using a Saga-based orchestration.}}
    %     \resumeItem{\normalsize{Strengthened system resilience by implementing a multi-tier retry strategy and Dead Letter Queues (DLQ) in Kafka, ensuring zero data loss and automated recovery during intermittent failures.}}
    %     \resumeItem{\normalsize{Ensured data consistency between MySQL and Kafka by adopting the Transactional Outbox pattern, guaranteeing that every financial state change is reliably published and processed.}}
    %     \resumeItem{\normalsize{Successfully mitigated Kafka consumer lag issues during high-traffic periods by scaling topic partitions and optimizing consumer-side processing logic, significantly improving message throughput.}}
    %   \resumeItemListEnd

    % \resumeProjectHeading
    %   {\textbf{Next Gen Platform CN3 Taxi} $|$ \small{Golang, Java, AWS, Kafka, ActiveMQ, MongoDB, Postgres}}{10/2023 -- Present}
    %   \resumeItemListStart
    %     \resumeItem{\normalsize{Developed a cloud-native microservices platform for taxi dispatching, focusing on scalability, high availability, and secure dispatching logic.}}
    %     \resumeItem{\normalsize{Enhanced system performance and scalability by optimizing data organization and improving asynchronous communication workflows.}}
    %   \resumeItemListEnd

  \resumeProjectListEnd
\vspace{-12pt}

%-----------CERTIFICATIONS & LANGUAGES-----------
\section{\color{airforceblue}CERTIFICATIONS \& LANGUAGES}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Certificates:}{ AWS Certified Developer -- Associate (AWS, 10/2023), Outstanding Contribution (GDG Cloud, 04/2023), Excellent Project (Solana Vietnam Coding Camp, 12/2022)} \\
     \vspace{2pt}
     \textbf{Languages:}{ IELTS 6.5, TOEIC (~800/900)}
    }}
 \end{itemize}
 \vspace{-12pt}

%-----------HONORS & AWARDS-----------
\section{\color{airforceblue}HONORS \& AWARDS}
  \resumeHonorListStart
    \resumeHonorHeading
      {\textbf{Bronze Medal} -- Vietnam Student Olympiad in Informatics (National Level)}{2019}
    \resumeHonorHeading
      {\textbf{Facilitator Engineer} - Google Cloud}{2022-2025}
    \resumeHonorHeading
      {\textbf{SAKURA SCIENCE Exchange Student} - Japan Science and Technology}{2023}
    \resumeHonorHeading
      {\textbf{Outstanding Performance \& 1st Runner Up Hacker Competition} -- Zalopay}{2025}
    \resumeHonorHeading
      {\textbf{Top 20 Coding Contest  Weekly Challenge} -- LeetCode}{2023}
    \resumeHonorHeading
      {\textbf{GDSC Hackathon (Google)} -- Top 22 Project}{Apr 2023}
    \resumeHonorHeading
      {\textbf{EVN Scholarship} -- Top 100 Highest Academic Achievement Award}{2022 -- 2023}
    \resumeHonorHeading
      {\textbf{Excellent Youth Award} -- VNU-HCM University of Science}{Mar 2023}
    \resumeHonorHeading
      {\textbf{Most Contributor Developer} -- FPT Corporation}{Sep 2023}
    \resumeHonorHeading
      {\textbf{Head of Fullstack Team} -- GDSC-HCMUS}{05/2022 -- 05/2023}
    \resumeHonorHeading
      {\textbf{Head of Engineer Team} -- ITConnectUS}{02/2022 -- 12/2023}
  \resumeHonorListEnd

\vspace{-12pt}

\end{document}
